---
title: "p8105_hw1_lvr2115"
author: "laura"
date: "2023-09-23"
output: github_document
---
#  Problem 1

```{r}
library(moderndive)
library(tidyverse)
data("early_january_weather")
str(early_january_weather)
```

The dataset is a subset of hourly meterological data from LGA, JFK, and EWR airports for January 2013. This dataset `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns. The 15 variables are `r ls(early_january_weather)`.

The mean of the temperature variable is `r mean(pull(early_january_weather, temp))`. 

This is a scatterplot showing the temperature at different hours during days in early January. The color of the data point shows the humidity. It is apparent that temperature fluctuates during the day and temperatures increase during the second week and. third week of january compared to the first. 

```{r scatterplot}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()
ggsave('temp_plot.png', width=6, height=4,dpi=300)
```
