---
title: "p8105_hw1_lvr2115"
author: "laura robles-torres"
date: "2023-09-23"
output: github_document
---
#  Problem 1

```{r}
library(moderndive)
library(tidyverse)
data("early_january_weather")
str(early_january_weather)
```

## Description of this dataset
The dataset is a subset of hourly meterological data from LGA, JFK, and EWR airports for January 2013. This dataset `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns. The 15 variables are `r ls(early_january_weather)`.

The mean of the temperature variable is `r mean(pull(early_january_weather, temp))`. 

This scatterplot showing the temperature at different hours of the day between January 1 and January 15. The color of the data point shows the relative humidity recorded at the same time and day. It is apparent that temperature fluctuates during the day, temperatures increase during the second week and compared to the first week. Humidity levels and temperatures are both higher on and around January 14.  

```{r scatterplot}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point() +
  xlab("Date and hour of recording") +ylab("Temperature in Fahrenheit")
ggsave('temp_plot.png', width=6, height=4,dpi=300)
```
#  Problem 2

This code chunk creates a data frame comprised of a random sample of size 10 from a standard Normal distribution, a logical vector indicating whether elements of the sample are greater than 0, a character vector of length 10, and a factor vector of length 10, with 3 different factor “levels”.

## Creating new data frame

```{r new_df_create}
new_df = tibble(
  samp = rnorm(10, sd = 1),
  vec_logical = samp > 0,
  vec_char = c("x", "y","z","aa","bb","cc","dd","ee","ff","gg"),
  vec_factor = factor(rep(c("nvr smk", "pst smk", "cur smk"), length.out = 10))
)
```

In this next code chunk, I am trying to take the mean of each variable in my dataframe new_df. 

## Taking the means of each new variables

```{r var_means}
mean_samp = mean(pull(new_df, samp))
  mean_samp
mean_log = mean(pull(new_df, vec_logical))
  mean_log
mean_char = mean(pull(new_df, vec_char))
mean_factor = mean(pull(new_df, vec_factor))
```

I was unable to take the mean of vec_char and vec_factor (returning 'NA' warning) because these are not numeric variables and this is not supported. 

## Converting variables from one type to another 
```{r var_conversions}
as.numeric(pull(new_df,vec_logical))
as.numeric(pull(new_df,vec_char))
as.numeric(pull(new_df,vec_factor))
```

Applying the as.numeric function to the logical and factor variables coerced their values into numbers corresponding to the different levels. The logical variable values output is now '0' and '1', while the factor variable values output is '1', '2', and '3', corresponding to the 3 levels. Applying the as.numeric function to the character variable returns `NA`, as it did when trying to take the means of this variable. The values of this variable cannot be coerced into numereric values. Output not shown. 